---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r loaddata,echo=TRUE}
activity <- read.csv("activity.csv", stringsAsFactors = FALSE)
activity[,2] <- as.Date(activity[,2], "%Y-%m-%d")

```

## What is mean total number of steps taken per day?

### Total number of steps taken perday 
```{r totalno,echo=TRUE}
sum.steps <- aggregate(x = activity[, 1], by=list(activity[, 2]), FUN=(function(x) sum(x, na.rm = FALSE)))
head(sum.steps)

```

### Histgram of the total number of steps taken each day
```{r histgram,echo=TRUE}
#Histgram of the total number of steps taken each day
hist(sum.steps[, 2],breaks=10, main="Frequency of Step Taken",xlab="Steps taken per day")
```

###Mean of the total number taken per day 
```{r mean,echo=TRUE}
mean.sum.steps <- mean(sum.steps[,2], na.rm=TRUE)
print(mean.sum.steps)
```

###Median of the total number taken per day 
```{r median,echo=TRUE}
median.sum.steps <- median(sum.steps[,2], na.rm=TRUE)
print(median.sum.steps)
```

## What is the average daily activity pattern?

### Time Series Plot
```{r timeseries, echo=TRUE}
mean.steps <- aggregate(x = activity[, 1], by=list(activity[, 2]), FUN=(function(x) mean(x, na.rm = FALSE)))

plot(mean.steps[, 1], mean.steps[,2], type="l", xlab = "Day", ylab = "Steps Taken", main = "Steps Taken Each Day")

```

### Maximum number of steps
```{r maximum, ech=TRUE }
activity[which.max(activity[,1]), 3]
```


## Imputing missing values

###Number of missing value
```{r na1,echo=TRUE}
sapply(activity, function(x) sum(is.na(x)))
```

### Fill the missing value with the mean of steps takeneach day
```{r na2,echo=TRUE}
#Fill the missing value of average steps each day with the mean of the average steps taken each day
mean.steps[is.na(mean.steps[,2]),][,2] <- mean(mean.steps[,2], na.rm=TRUE)

#replace the missing value for each interval with the average steps each day.
clean.activity <- activity 
for (i in 1:nrow(clean.activity)) {
        if(is.na(clean.activity[i, 1])){
                clean.activity[i, 1] <- mean.steps[which(mean.steps$Group.1==clean.activity[i, 2]), 2]
        }
                
}


```
###New dataset
```{r newdata, echo=TRUE}
head(clean.activity)
```

###Histgram of the total number of steps taken each day 
```{r histgram2, echo=TRUE}
sum.clean.steps <- aggregate(x = clean.activity[, 1], by=list(clean.activity[, 2]), FUN=(function(x) sum(x, na.rm = FALSE)))
hist(sum.clean.steps[,2], breaks = 10, main="Frequency of Step Taken",xlab="Steps taken per day")

```

###Mean of the total number taken per day 
```{r mean1,echo=TRUE}
mean.sum.clean.steps <- mean(sum.clean.steps[,2], na.rm=TRUE)
print(mean.sum.clean.steps)
```

###Median of the total number taken per day 
```{r median1,echo=TRUE}
median.sum.clean.steps <- median(sum.clean.steps[,2], na.rm=TRUE)

print(median.sum.clean.steps)
```
## Are there differences in activity patterns between weekdays and weekends?

###Create weekday variables
```{r weekday, echo=TRUE}
wdays<- c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday')
clean.activity$weekdays <- factor((weekdays(clean.activity$date) %in% wdays), levels = c(FALSE, TRUE), labels=c("weekend", "weekday"))

```
###plot 
```{r plot2, echo=TRUE, warning=FALSE}
require(ggplot2)
qplot(interval, steps, data=clean.activity, facets=weekdays~.,geom = "line")
```









